ElasticNet and Lasso

### 2021-12-20 03_analysis/ElasticNet.Rmd
added variable transformations

>>>>

# MW: added variable transformations
library(tidyverse)
data <- data %>%
  mutate(
    income = gdp / pop
  ) %>%
  mutate_at(
    c("aid", "count", "gdp", "income", "pop", "unemp",
      "disaster", "dist", "distw", 
      "distwces", "trade", "china_gdp"),
    asinh # use inverse hyperbolic sine rather than log(1 + x)
  ) %>%
  group_by(recipient_iso3) %>%
  mutate(
    aid = lead(aid, by = "year"),
    lead_count = lead(count, by = "year")
  ) %>%
  ungroup %>%
  na.omit
